---
title: "Midterm 2 Code and Answers"
format: pdf
editor: visual
---

```{r}
library(forecast)
library(here)
library(readxl)
```

```{r}
dat <- read_excel(here::here("Course Files/Data for Exam 2.xlsx"), sheet = "Sales")
```

##Prob 2 ###A

```{r}
y <- dat$Sales
plot(y)

z <- diff(y, differences = 1)
plot(z)
```

###B

```{r}
acf(z)
pacf(z)
```

-   AR(2), there is a sudden jump towards 0 in the PACF whereas in ACF there is a gradual oscillation towards 0

-   MA(3), could claim that ACF has 3 non-zero values and that PACF declines towards 0, changed to MA(2) since the 3rd MA value was not significant

-   ARMA(1,1), could claim that both acf and pacf are gradually declining towards 0

```{r}
mod1 <- Arima(y, order = c(2, 1, 0)); summary(mod1)

mod2 <- Arima(y, order = c(0,1,2)); summary(mod2)

mod3 <- Arima(y, order = c(1,1,1)); summary(mod3)
```

###C

```{r}
e1 <- residuals(mod1)
n1 <- length(e1)
k1 <- 2 #for p
Box.test(e1, type = "Ljung", lag = 8, fitdf = k1)

e2 <- residuals(mod2)
n2 <- length(e2)
k2 <- 2 #for p
Box.test(e2, type = "Ljung", lag = 8, fitdf = k2)

e3 <- residuals(mod3)
n3 <- length(e3)
k3 <- 2 #for p
Box.test(e3, type = "Ljung", lag = 8, fitdf = k3)
```

###D

```{r}
AIC1 <- exp(2*k1/n1) * (sum(e1^2))/n1; AIC1
BIC1 <- (n1^(k1/n1)) * (sum(e1^2))/n1; BIC1

AIC2 <- exp(2*k2/n2) * (sum(e2^2))/n2; AIC2
BIC2 <- (n2^(k2/n2)) * (sum(e2^2))/n2; BIC2

AIC3 <- exp(2*k3/n3) * (sum(e3^2))/n3; AIC3
BIC3 <- (n3^(k3/n3)) * (sum(e3^2))/n3; BIC3

```

Model 2 (the MA(2) model), appears to be the best model in both the computer-generated and hand-calculated AIC/BIC values.

###E

```{r}
forecast(mod2, h = 3)
```

##Prob 3 ###A

```{r}
dat <- read_excel("C:/Users/Nils Berzins/OneDrive/Desktop/Cal Poly/2022-2023/Spring Quarter/ECON 406/Course Files/Data for Exam 2.xlsx", sheet = "Googl")
```

```{r}
y <- dat$Price

ty <- y[1:180]
vy <- y[181:220]
```

```{r}
diff_series <- diff(ty, differenes = 1)
log_diff_series <- diff(log(ty), differences = 1)

plot(diff_series)
plot(log_diff_series)
```

```{r}
acf(diff_series)
pacf(diff_series)
```

-   MA(1)

-   ARMA(1, 7)

-   

```{r}
acf(log_diff_series)
pacf(log_diff_series)
```

```{r Model 1 - Differenced Series}

Mod1 <- Arima(ty, order = c(0, 1, 1)); summary(Mod1)

Mod2 <- Arima(ty, order = c(7, 1, 1)); summary(Mod2)

Mod2b <- Arima(ty, order = c(7, 1, 1), fixed = c(0, 0, 0, 0, 0, 0, NA, 0)) 
summary(Mod2b)
```

```{r}
e1 <- residuals(Mod1)
n1 <- length(e1)
k1 <- 1 #for p
Box.test(e1, type = "Ljung", lag = 12, fitdf = k1)

e2 <- residuals(Mod2)
n2 <- length(e2)
k2 <- 8 # 1 for p and 7 for q
Box.test(e2, type = "Ljung", lag = 12, fitdf = k2)

e2b <- residuals(Mod2b)
n2b <- length(e2b)
k2b <- 1 #for q
Box.test(e2b, type = "Ljung", lag = 12, fitdf = k2b)
```

```{r Model 2 - Log Differenced Series}
Mod1l <- Arima(log(ty), order = c(0, 1, 1)); summary(Mod1)

Mod2l <- Arima(log(ty), order = c(7, 1, 1)); summary(Mod2)

Mod2bl <- Arima(log(ty), order = c(7, 1, 1), fixed = c(0, 0, 0, 0, 0, 0, NA, 0)) 
summary(Mod2b)

```

```{r}
e1l <- residuals(Mod1l)
n1l <- length(e1l)
k1l <- 1 #for p
Box.test(e1l, type = "Ljung", lag = 12, fitdf = k1l)

e2l <- residuals(Mod2l)
n2l <- length(e2l)
k2l <- 8 # 1 for p and 7 for q
Box.test(e2l, type = "Ljung", lag = 12, fitdf = k2l)

e2bl <- residuals(Mod2bl)
n2bl <- length(e2bl)
k2bl <- 1 #for q
Box.test(e2bl, type = "Ljung", lag = 12, fitdf = k2bl)
```

-   the constrained version of both tests is the preferred version

###B

```{r}
AIC2b <- exp(2*k2b/n2b) * (sum(e2b^2))/n2b; AIC2b
BIC2b <- (n2b^(k2b/n2b)) * (sum(e2b^2))/n2b; BIC2b

AIC2bl <- exp(2*k2bl/n2bl) * (sum(e2bl^2))/n2bl; AIC2bl
BIC2bl <- (n2bl^(k2b/n2bl)) * (sum(e2bl^2))/n2bl; BIC2bl
```

```{r}
refit2b <- Arima(vy, model = Mod2b)
accuracy(refit2b)

refit2bl <- Arima(log(vy), model = Mod2bl)
accuracy(refit2bl)
```

###C

```{r}
mod2bl_full <- Arima(log(y), order = c(7, 1, 1), fixed = c(0, 0, 0, 0, 0, 0, NA, 0)) 

f2bl <- forecast(mod2bl_full, h = 2)

exp(f2bl$mean)
```
